%-------------------------
% Resume in Latex
% Author : Yasar Nazzarian
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Yasar Nazzarian} & Email : \href{mailto:yasar20111926@hotmail.com}{yasar20111926@hotmail.com} \\
  LinkedIn: \href{https://www.linkedin.com/in/yasarnazzarian-98}{yasarnazzarian-98} & Mobile : +1-514-652-7081 \\
  GitHub: \href{https://www.github.com/Yasar2019}{Yasar2019} & \\
\end{tabular*}


%-----------ABOUT-----------------
\section{About}
Recent Software Engineering graduate from École de Technologie Supérieure with hands-on experience in AI integration, software development, and cloud computing. Proven track record in delivering scalable solutions using microservices architecture and Kubernetes, and a strong foundation in automated testing and continuous integration.

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeItem{Programming Languages \& SE Principles}
      {Java, C, Python, SQL, JavaScript, OOP, Design Patterns, Agile (Scrum, Kanban), TDD}
    \resumeItem{Software Applications \& Tools}
      {Hadoop, Apache Spark, Jupyter, Microsoft Azure, Git, Docker, Terraform, Maven, Arduino, QALab, Junit, Cisco Packet Tracer, Visual Studio, Microsoft Office}
    \resumeItem{Frameworks \& Libraries}
      {Spring Boot, React, Flask, Pytorch, Numpy, Pandas, OpenCV, Sklearn}
    \resumeItem{Technologies}
      {Microservices Architecture, Apache Kafka, RabbitMQ, RESTful APIs, CI/CD}
    \resumeItem{Operating Systems}
      {Windows, Linux}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {École de Technologie Supérieure}{Montreal, QC}
      {Bachelor of Engineering in Software Engineering}{2020 -- 2024}
    \resumeSubheading
      {National Taipei University of Technology}{Taipei, Taiwan}
      {Exchange Program (Computer Science)}{Sept. 2023 -- Jan. 2024}
    \resumeSubheading
      {Montmorency College}{Laval, QC}
      {Diploma of Collegial Studies in Natural Science}{Aug. 2017 -- July 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Shared Services Canada}{Montreal, QC}
      {Software Support Analyst}{May 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Power Apps and Power BI Support}
          {Provided technical support for Power Apps and Power BI.}
        \resumeItem{Interactive Dashboards}
          {Developed solutions using PowerPlatform, and created interactive dashboards for data-driven decision-making.}
      \resumeItemListEnd

    \resumeSubheading
      {Shared Services Canada}{Montreal, QC}
      {Software Intern}{Feb 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{Solutions Development}
          {Developed new solutions using Microsoft PowerPlatform Tools.}
        \resumeItem{Data Models}
          {Analyzed business requirements to design data models converting raw data into meaningful information.}
        \resumeItem{Dashboards}
          {Created interactive dashboards and reports using Power BI for data-driven decision making.}
      \resumeItemListEnd

    \resumeSubheading
      {Ville de Laval}{Montreal, QC}
      {IT Intern}{Winter 2023}
      \resumeItemListStart
        \resumeItem{AI Integration}
          {Integrated AI solutions into existing systems and provided detailed technical analysis and support.}
      \resumeItemListEnd

    \resumeSubheading
      {Delight Canada}{Montreal, QC}
      {Software Developer}{Summer 2022}
      \resumeItemListStart
        \resumeItem{Microservices}
          {Developed microservices for controlling horticulture lighting systems.}
        \resumeItem{Bluetooth Control}
          {Programmed an ESP32-WROOM for controlling LED panels using Bluetooth Mesh.}
        \resumeItem{ERP Enhancements}
          {Enhanced functionalities of the ERP system (Odoo).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Microservices for STM \& TomTom Data Integration}
      {Developed a microservice architecture to compare travel times between bus services; implemented telemetry mechanics to monitor real-time bus data and optimize service performance.}
    \resumeSubItem{TBrain Competition: Go Power Imitation}
      {Built machine learning networks using CNN, RNN, LSTM for Go game imitation and play style identification.}
    \resumeSubItem{Remote-Controlled Miniature Crane}
      {Modeled parts using G-Code, MasterCam, and created electrical circuits (PCBs) using Altium; programmed the microcontroller for bidirectional communication.}
  \resumeSubHeadingListEnd


%--------CERTIFICATIONS------------
\section{Licenses and Certifications}
 \resumeSubHeadingListStart
   \item{
     \textbf{Microsoft Certified: Azure AI Fundamentals} \href{https://www.credly.com/badges/1755ae09-3878-4274-bb2d-88e292cd0b5b?source=linked_in_profile}{(View Certificate)}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}